National Pipeline System as a Solution to Future Water Shortage in the United States

### 2013-02-04 paper.tex
edits

As a result, we firmly recommend that the entirety of our proprosed
infrastructure developments, particularly the national pipeline network,
be implemented over the upcoming years.
\begin{thebibliography}{10}
\bibitem{key-1}Cai, X., Cline, S., Rosegrant, M. (2002). Global Water
Outlook to 2025. \emph{International Food Policy Research Institute.}

>>>>

As a result, we firmly recommend that the entirety of our proposed
infrastructure developments, particularly the national pipeline network,
be implemented over the upcoming years.
\begin{thebibliography}{10}
\bibitem{key-1}Cai, X., Cline, S., Rosegrant, M. (2002). Global Water
Outlook to 2025. \emph{International Food Policy Research Institute.}
